Supplemental Information

### 2021-07-27 manuscript/supplement.Rmd
finish revision of draft

<br>

@@

(ref:s7) (**A**) Metabolic flux model of LF metabolism in 21% oxygen.  (**B**) Metabolic flux model of PASMC metabolism in 21% oxygen. (**C**) LF fluxes were normalized to cell growth rate. Graph depicts the ratio of normalized metabolic fluxes in LFs cultured in 0.5% oxygen compared to 21% oxygen control. Fluxes with non-overlapping confidence intervals are highlighted to indicate significant changes. (**D**) Ratio of metabolic fluxes in 0.5% oxygen compared to 21% oxygen in PASMCs.

Supplementary Figure 1: (ref:s1)

Supplementary Figure 2: (ref:s2)

Supplementary Figure 3: (ref:s3)

Supplementary Figure 4: (ref:s4)

Supplementary Figure 5: (ref:s5)

Supplementary Figure 6: (ref:s6)

Supplementary Figure 7: (ref:s7)

@@

>>>>

@@

(ref:s7) **Isotopically non-stationary metabolic flux analysis.** (**A**) Metabolic flux model of LF metabolism in 21% oxygen.  (**B**) Metabolic flux model of PASMC metabolism in 21% oxygen. (**C**) LF fluxes were normalized to cell growth rate. Graph depicts the ratio of normalized metabolic fluxes in LFs cultured in 0.5% oxygen compared to 21% oxygen control. Fluxes with non-overlapping confidence intervals are highlighted to indicate significant changes. (**D**) Ratio of metabolic fluxes in 0.5% oxygen compared to 21% oxygen in PASMCs.

(ref:s8) **Metabolomic profiling of hypoxia and BAY treated lung fibroblasts.** (**A**, **B**) Volcano plots of differentially regulated metabolites with 0.5% oxygen in DMSO-treated cells (A) or BAY treatment in 21% oxygen-cultured cells (B). Significantly increased metabolites with 0.5% oxygen (*blue*) or with BAY treatment (*purple*) are indicated. The top 10 up- and down-regulated metabolites are labeled. (**C**) Venn diagram illustrating the number of differentially regulated metabolites following hypoxia (*blue*) or BAY treatment (*purple*). (**D**, **E**) Results of a metabolite set enrichment analysis of KEGG pathways based on the data from (A) and (B). Significantly enriched pathways with p < 0.05 are indicated.

(ref:s9) **Transcriptomic profiling of hypoxia and BAY treated lung fibroblasts.** (**A**)

```{r}
figs <- 
  list.files(
    system.file(
      "manuscript/figures", 
      package = "Copeland.2021.hypoxia.flux"
    ), 
    pattern = "s\\d{1}\\.pdf"
  ) %>% 
  rlang::set_names(stringr::str_extract(., "^.*(?=\\.pdf)"))
```

```{r results = "asis"}
out <- 
  purrr::imap(
    figs, 
    ~ cat("Supplementary Figure ", stringr::str_extract(.y, "\\d"), ": (ref:", .y, ")\n\n", sep = "")
  )
```

@@

```{r s7, fig.cap = "(ref:s7)"}
knitr::include_graphics(
  system.file(
    "manuscript/figures/s7.pdf",
    package = "Copeland.2021.hypoxia.flux"
  )
)
```

```{r s8, fig.cap = "(ref:s8)"}
knitr::include_graphics(
  system.file(
    "manuscript/figures/s8.pdf",
    package = "Copeland.2021.hypoxia.flux"
  )
)
```

```{r s9, fig.cap = "(ref:s9)"}
knitr::include_graphics(
  system.file(
    "manuscript/figures/s9.pdf",
    package = "Copeland.2021.hypoxia.flux"
  )
)
```
